Papers I Love

### 2017-04-03 texts/dev/PapersILove.tex
process algebra paper
j armstrong paper on forecasting
process algebrapaper

\subsubsection{Distributed Systems}
\begin{enumerate}
	\item {Time, Clocks and the Ordering of Events in a Distributed System\\		
\href{http://academic.research.microsoft.com/Publication/775212/time-clocks-and-the-ordering-of-events-in-a-distributed-system}{http://academic.research.microsoft.com/Publication/775212/time-clocks-and-the-ordering-of-events-in-a-distributed-system}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html#time-clocks}{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html\#time-clocks}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/time-clocks.pdf}{http://research.microsoft.com/en-us/um/people/lamport/pubs/time-clocks.pdf}}
	\item {Distributed Snapshots: Determining Global States of Distributed Systems\\
\href{http://academic.research.microsoft.com/Publication/803548/distributed-snapshots-determining-global-states-of-distributed-systems}{http://academic.research.microsoft.com/Publication/803548/distributed-snapshots-determining-global-states-of-distributed-systems}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html#chandy}{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html\#chandy}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/chandy.pdf}{http://research.microsoft.com/en-us/um/people/lamport/pubs/chandy.pdf}}
	\item {Your Coffee Shop Doesn’t Use Two-Phase Commit\\
\href{http://www.enterpriseintegrationpatterns.com/docs/IEEE_Software_Design_2PC.pdf}{http://www.enterpriseintegrationpatterns.com/docs/IEEE\_Software\_Design\_2PC.pdf}}
	\item {A Brief History of Process Algebra\\
\url{http://alexandria.tue.nl/extra1/wskrap/publichtml/200402.pdf}}
	\item {Life Beyond Distributed Transactions: An Apostate’s Opinion\\
\url{http://www.ics.uci.edu/~cs223/papers/cidr07p15.pdf}}
\end{enumerate}

@@

\subsection{Programming Paradigms}
\subsubsection{Object Oriented}
\begin{enumerate}
	\item {A Theory of Objects\\
\url{http://academic.research.microsoft.com/Publication/1354440/a-theory-of-objects}\\
\url{http://lucacardelli.name/Talks/1997-06\%20A\%20Theory\%20of\%20Object\%20(ECOOP\%20Tutorial).pdf}}
	\item {Traits: Composable Units of Behaviour\\
\url{http://scg.unibe.ch/archive/papers/Scha03aTraits.pdf}}
	\item {Applying Traits to the Smalltalk Collection Hierarchy\\
\url{http://www.researchgate.net/publication/2564879_Applying_Traits_to_the_Smalltalk_Collection_Hierarchy}}
	\item {A Laboratory for Teaching Object-Oriented Thinking\\
\url{http://www.inf.ed.ac.uk/teaching/courses/seoc/2007_2008/resources/CRC_OOthinking.pdf}}
\end{enumerate}
\subsubsection{Double Dispatch}
\begin{enumerate}
	\item {Design and evaluation of C++ open multi-methods\\
\url{https://parasol.tamu.edu/~yuriys/papers/OMM10.pdf}}
\end{enumerate}

@@

\section{Mathematics}
\subsection{Real Analysis}
\begin{enumerate}
	\item {COISAS QUE O LUÍS PRECISA APRENDER\\
\url{http://www.todasasconfiguracoes.com/wp-content/uploads/2012/04/luis.pdf}}
\end{enumerate}
\subsection {Statistics}
\begin{enumerate}
	\item {A Note on the Generation of Random Normal Deviates\\
\url{http://projecteuclid.org/euclid.aoms/1177706645}}
	\item {Tidy Data\\
\url{http://vita.had.co.nz/papers/tidy-data.pdf}}
	\item {A Tutorial on Principal Component Analysis - Derivation, Discussion and Singular Value Decomposition\\
\url{https://www.cs.princeton.edu/picasso/mats/PCA-Tutorial-Intuition_jp.pdf}}
	\item{An introduction to ROC analysis\\
\url{https://ccrma.stanford.edu/workshops/mir2009/references/ROCintro.pdf}}
\end{enumerate}

>>>>

\subsubsection{Distributed Systems}
\begin{enumerate}
	\item {Time, Clocks and the Ordering of Events in a Distributed System\\		
\href{http://academic.research.microsoft.com/Publication/775212/time-clocks-and-the-ordering-of-events-in-a-distributed-system}{http://academic.research.microsoft.com/Publication/775212/time-clocks-and-the-ordering-of-events-in-a-distributed-system}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html#time-clocks}{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html\#time-clocks}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/time-clocks.pdf}{http://research.microsoft.com/en-us/um/people/lamport/pubs/time-clocks.pdf}}
	\item {Distributed Snapshots: Determining Global States of Distributed Systems\\
\href{http://academic.research.microsoft.com/Publication/803548/distributed-snapshots-determining-global-states-of-distributed-systems}{http://academic.research.microsoft.com/Publication/803548/distributed-snapshots-determining-global-states-of-distributed-systems}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html#chandy}{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html\#chandy}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/chandy.pdf}{http://research.microsoft.com/en-us/um/people/lamport/pubs/chandy.pdf}}
	\item {Your Coffee Shop Doesn’t Use Two-Phase Commit\\
\href{http://www.enterpriseintegrationpatterns.com/docs/IEEE_Software_Design_2PC.pdf}{http://www.enterpriseintegrationpatterns.com/docs/IEEE\_Software\_Design\_2PC.pdf}}
	\item {Life Beyond Distributed Transactions: An Apostate’s Opinion\\
\url{http://www.ics.uci.edu/~cs223/papers/cidr07p15.pdf}}
\end{enumerate}

\subsubsection{Process Algebra}
\begin{enumerate}
	\item {A Brief History of Process Algebra\\
\url{http://alexandria.tue.nl/extra1/wskrap/publichtml/200402.pdf}}
	\item {Some of My Favourite Results in Classic Process Algebra (Version of September 9, 2003)\\
\url{https://www.researchgate.net/publication/228785318_Some_of_My_Favourite_Results_in_Classic_Process_Algebra_Version_of_September_9_2003}}
\end{enumerate}

@@

\subsection{Programming Paradigms}
\subsubsection{Process Theory}
\begin{enumerate}
	\item {A Brief History of Process Algebra\\
\url{http://alexandria.tue.nl/extra1/wskrap/publichtml/200402.pdf}}
\end{enumerate}
\subsubsection{Object Oriented}
\begin{enumerate}
	\item {A Theory of Objects\\
\url{http://academic.research.microsoft.com/Publication/1354440/a-theory-of-objects}\\
\url{http://lucacardelli.name/Talks/1997-06\%20A\%20Theory\%20of\%20Object\%20(ECOOP\%20Tutorial).pdf}}
	\item {Traits: Composable Units of Behaviour\\
\url{http://scg.unibe.ch/archive/papers/Scha03aTraits.pdf}}
	\item {Applying Traits to the Smalltalk Collection Hierarchy\\
\url{http://www.researchgate.net/publication/2564879_Applying_Traits_to_the_Smalltalk_Collection_Hierarchy}}
	\item {A Laboratory for Teaching Object-Oriented Thinking\\
\url{http://www.inf.ed.ac.uk/teaching/courses/seoc/2007_2008/resources/CRC_OOthinking.pdf}}
\end{enumerate}
\subsubsection{Double Dispatch}
\begin{enumerate}
	\item {Design and evaluation of C++ open multi-methods\\
\url{https://parasol.tamu.edu/~yuriys/papers/OMM10.pdf}}
\end{enumerate}

@@

\section{Mathematics}
\subsection{Real Analysis}
\begin{enumerate}
	\item {COISAS QUE O LUÍS PRECISA APRENDER\\
\url{http://www.todasasconfiguracoes.com/wp-content/uploads/2012/04/luis.pdf}}
\end{enumerate}
\subsection {Statistics}
\begin{enumerate}
	\item {A Note on the Generation of Random Normal Deviates\\
\url{http://projecteuclid.org/euclid.aoms/1177706645}}
	\item {Tidy Data\\
\url{http://vita.had.co.nz/papers/tidy-data.pdf}}
	\item {A Tutorial on Principal Component Analysis - Derivation, Discussion and Singular Value Decomposition\\
\url{https://www.cs.princeton.edu/picasso/mats/PCA-Tutorial-Intuition_jp.pdf}}
	\item{An introduction to ROC analysis\\
\url{https://ccrma.stanford.edu/workshops/mir2009/references/ROCintro.pdf}}
\end{enumerate}
\subsection{Forecast}
\begin{enumerate}
	\item {Forecasting Global Climate Change\\
\url{https://faculty.wharton.upenn.edu/wp-content/uploads/2015/02/GlobalClimateChange-FWP-(2)_2.pdf}}
\end{enumerate}
